Computing Exact Restricted Isometry Constants via Mixed Integer Semidefinite Programming

### 2016-03-21 RIP-MISDP-Paper/IEEE_RIP-MISDP.tex
added explanation about solved instances for MISDP and quality of exact RICS in appendix

The tests were performed on a Linux cluster with Intel i3 CPUs with 3.2GHz, 4MB cache, and 8GB memory running
Linux. Each computation was performed single-threaded with a single process running on each computer and with 
a time limit of four hours. The code was compiled with gcc 4.4.5 with \texttt{-O3} optimization. For 39 matrices 
the evaluation of~\eqref{Asp08Dual} was aborted for all 15 choices of $\rho$, because of the memory limit of 8GB. 
These are counted with the maximum allowed time of four hours.

@@

>>>>

The tests were performed on a Linux cluster with Intel i3 CPUs with 3.2GHz, 4MB cache, and 8GB memory running
Linux. Each computation was performed single-threaded with a single process running on each computer and with 
a time limit of four hours. The code was compiled with gcc 4.4.5 with \texttt{-O3} optimization. For 39 matrices 
the evaluation of~\eqref{Asp08Dual} was aborted for all 15 choices of $\rho$, because of the memory limit of 8GB.
\color{red}We also failed to solve \eqref{MISDP} for the left-hand side of the three medium sized rank one matrices with default
parameters because SDPA failed to solve the root node relaxation, however with different settings or a different
SDP-solver we could verify that $\alpha_k$ equaled zero up to the numerical tolerance for these instances.\color{black}
These are counted with the maximum allowed time of four hours.

@@

\color{red}The restricted isometry constants of all matrices can be found in the appendix. Note that for the unscaled matrices
the restricted isometry constants can be expected to be much larger than for the scaled ones. Furthermore, since we solved
the instances with a feasibility tolerance of $10^{-6}$, which influences the optimal objective by a factor of the
largest objective coefficients and the number of variables, the computed constants are only exact up to a factor
of about $10^{-2}$ for these matrices, while the precision is much better for the normalized ones because of their
smaller objective coefficients.\color{black}
